Formalizing Stack Safety as a Security Property

### 2021-10-01 submission4/main.tex
Tighten up stuff

This section explains our formal stack safety properties through a series
of examples, each presented both in C syntax and in corresponding assembly code for a
simple imaginary two-address machine (see Figure~\ref{fig:int1}).
The address of each instruction is shown to its left.
The assembly code reflects a simple compilation strategy in which
local variables are stored in consecutive slots of the stack frame.
For the moment, arguments and return values are passed in registers.
The stack grows upward in
memory and {\tt \%sp} points to the first unused word above the top of the stack.
The {\tt call} and {\tt ret} instructions push and pop the return address from the stack,
implicitly adjusting the stack pointer.
At the right of each example, we show snapshots of the layout of stack memory just before
selected instructions (labeled by their addresses) are executed; each box represents a memory word
(the machine is word addressed), and addresses increase to the right.
We refer to registers and addresses collectively as {\em state elements} or just elements.
  %% \bcp{Most of the
  %% figure is kind of self-explanatory with this help, but the rightmost part
  %% is a little opaque: what do 2, 3, 11, 12 mean?  What is SP?  What are the
  %% numbers in the boxes?  What are these brackets under the boxes, ...  One
  %% simple thing we could do to help might be to label the right-hand column
  %% something like ``Snapshots,'' or at least explain early on in the text
  %% that this is what they are.}

@@

\begin{tabular}{l}
{\sc Call} \\
\judgmenttwobrlong[]
              {\(\codemap ~ (\mach ~ \PCname) = \callmap\)}
%             {\(\components = \sealcon ~ \mach\)}
              {\(\components = \{\component | \sealcon ~ \mach[\component]\}\)}
              {\(\domMap' = \domMap[\components \mapsto \sealed{|\rts|}]\)}
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\retcon ~ \mach)::\rts\)} \\
\end{tabular}
\begin{tabular}{l}
{\sc ReturnFound} \\
\judgmenttwo[]
            {\(\mach \stepsto \mach' \in \target\)}
            {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
            {\(\mach,(\domMap,\target::\rts) \stepsto_C \domMap[\components \mapsto \unsealed],\rts\)} \\
{\sc ReturnRec} \\
\end{tabular}
\begin{tabular}{l}
\judgmentbr[]
            {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
            {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
            {\(\mach,(\domMap,\underscore::\rts) \stepsto_C \domMap'[\components \mapsto \unsealed],\rts'\)} \\
\end{tabular}
\begin{tabular}{l}
\end{tabular}

>>>>

This section explains our formal stack safety properties through a series
of examples, each presented both in C syntax and in corresponding assembly code for an
imaginary two-address machine (see Figure~\ref{fig:int1}).
Each instruction's address is shown to its left.
The assembly code reflects a simple compilation strategy in which
local variables are stored in consecutive slots of the stack frame.
For the moment, arguments and return values are passed in registers.
The stack grows upward in
memory and {\tt \%sp} points to the first unused word above the top of the stack.
The {\tt call} and {\tt ret} instructions push and pop the return address from the stack,
implicitly adjusting the stack pointer.
At the right of each example, we show snapshots of the layout of stack memory just before
selected instructions (labeled by address) are executed; each box represents a memory word
(the machine is word addressed). Addresses increase to the right.
We refer to registers and addresses collectively as {\em state elements} or just elements.
  %% \bcp{Most of the
  %% figure is kind of self-explanatory with this help, but the rightmost part
  %% is a little opaque: what do 2, 3, 11, 12 mean?  What is SP?  What are the
  %% numbers in the boxes?  What are these brackets under the boxes, ...  One
  %% simple thing we could do to help might be to label the right-hand column
  %% something like ``Snapshots,'' or at least explain early on in the text
  %% that this is what they are.}

@@

\begin{tabular}{l}
  {\sc Call} \\
  \judgmenttwobrlong[]
                    {\(\codemap ~ (\mach ~ \PCname) = \callmap\)}
                    %             {\(\components = \sealcon ~ \mach\)}
                    {\(\components = \{\component | \sealcon ~ \mach[\component]\}\)}
                    {\(\domMap' = \domMap[\components \mapsto \sealed{|\rts|}]\)}
                    {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\retcon ~ \mach)::\rts\)} \\
\end{tabular}

\begin{tabular}{l}
  {\sc ReturnFound} \\
  \judgmenttwo[]
              {\(\mach \stepsto \mach' \in \target\)}
              {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
              {\(\mach,(\domMap,\target::\rts) \stepsto_C \domMap[\components \mapsto \unsealed],\rts\)} \\
              {\sc ReturnRec} \\
\end{tabular}

\begin{tabular}{l}
  \judgmentbr[]
             {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
             {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
             {\(\mach,(\domMap,\underscore::\rts) \stepsto_C \domMap'[\components \mapsto \unsealed],\rts'\)} \\
\end{tabular}
